\textsf{Are frontier models superhuman chemists?}

### 2024-03-14 src/tex/appendix.tex
update confidence score estimates
update plotting workflow

\begin{figure}
    \centering
    \includegraphics{figures/all_questions_models_completely_correct_radar.pdf}
    \caption{Caption}
    \label{fig:all_questions_models_completely_correct_radar}
    \script{analyze_model_reports.py}
\end{figure}

@@

\subsection{Confidence estimates}

@@

\Cref{XX} plots the distribution of those scores.

\begin{figure} 
    \centering
    \caption{\textbf{Distribution of confidence scores reported by \glspl{llm}.}} 
    \label{fig:confidence_score_distributions}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics{figures/all_questions_models_completely_correct_radar_overall.pdf}
    \caption{Caption}
    \label{fig:all_questions_models_completely_correct_radar_overall}
    \script{analyze_model_reports.py}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{figures/performance_per_topic.pdf}
    \caption{Caption}
    \label{fig:performance_per_topic}
    \script{analyze_performance_per_source.py}
\end{figure}

@@

\subsection{Confidence estimates} \label{sec:confidence_estimates}

@@

\Cref{fig:confidence_score_distributions} plots the distribution of those scores.

\begin{figure} 
    \centering
    \includegraphics{figures/confidence_score_distributions.pdf}
    \caption{\textbf{Distribution of confidence scores reported by \glspl{llm}.}} 
    \label{fig:confidence_score_distributions}
    \script{plot_confidence_score_distributions.py}
\end{figure}

### 2024-03-14 src/tex/ms.tex
update plotting workflow

In this spider chart, the worst score for every dimension is 0 (no question answered completely correctly) and the best score is 1 (all questions answered correctly). 
Thus, a larger colored area indicates a better performance. 
One can observe that this performance varies widely across models and topics. 
While computational chemistry and biochemistry receive relatively high scores for many models, this is not the cases for topics such as chemical safety or analytical chemistry.
In the subfield of analytical chemistry the prediction of the number of peaks observable in a \gls{nmr} spectrum proved difficult for the models (e.g., \SI{\variable{outputs/subset_scores/is_number_nmr_peaks_gpt-4.txt}}{\percent}). 
While this question is relatively easy (\SI{\variable{outputs/human_subset_scores/is_number_nmr_peaks.txt}}{\percent}) for trained humans given a drawing of the compounds, models that are only shown the \gls{smiles} string of a compound have to use this to reason about the symmetry of the compound. 
This is mirrored in the questions about point groups of compounds, which is models struggle with more than humans ().

>>>>

In this spider chart, the worst score for every dimension is 0 (no question answered completely correctly) and the best score is 1 (all questions answered correctly). 
Thus, a larger colored area indicates a better performance. 
One can observe that this performance varies widely across models and topics. 
While computational chemistry and biochemistry receive relatively high scores for many models, this is not the cases for topics such as chemical safety or analytical chemistry.
% In the subfield of analytical chemistry the prediction of the number of peaks observable in a \gls{nmr} spectrum proved difficult for the models (e.g., \variable{outputs/subset_scores/is_number_nmr_peaks_gpt-4.txt}. 
% While this question is relatively easy (\variable{outputs/human_subset_scores/is_number_nmr_peaks.txt}) for trained humans given a drawing of the compounds, models that are only shown the \gls{smiles} string of a compound have to use this to reason about the symmetry of the compound. 
% This is mirrored in the questions about point groups of compounds, which is models struggle with more than humans ().

% GFK performance -> would the models obtain a chemical license
